Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-16 paper.qmd
Updated Figure 5
Updated Figure 5 title

<!-- langevitour with pD model for two-curvy clusters -->
```{r}
#| label: best-fit-umap1
#| fig-cap: "Model in \\gD{} ($a_1 = 0.12$), on the layout and two views of the fit in projections from $7\\text{-}D$, for the two non-linear clusters data ($n =  2000$ and $p = 7$). One view shows the fitted model, and the other shows the fitted and true models alongside the data. The fitted model accurately represents the shape of the clusters but does not capture the edges of the structure. This illustrates a characteristic of tSNE, which compresses the data when transforming the data into \\gD{}. Video of the langevitour animations is available at <>."
#| fig-width: 10
#| fig-height: 10

>>>>

<!-- langevitour with pD model for two-curvy clusters -->
```{r}
#| label: best-fit-umap1
#| fig-cap: "We start with a tSNE layout (a) of non-linear clusters data ($n =  2000$ and $p = 7$), from which the \\gD{} wireframe is constructed (b) and then lifted to $7\\text{-}D$. A \\gD{} projection of the model fit from a tour through the $7\\text{-}D$ space is presented in c. Additionally, a \\gD{} projection of the fitted and true models (d) from the same tour demonstrates that the model accurately captures the non-linear structure of the data, although it does not fully represent the width of that structure. This highlights a key characteristic of tSNE, which compresses the data when applying tSNE. Furthermore, the sparse space observed in the middle of the tSNE layout is a result of (hyper-parameter) choice. The default is used. Video of the langevitour animation is available at <>."
#| fig-width: 10
#| fig-height: 10
